---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---

```{r}
data <- read.csv("./Gender_Height_Weight_Index.csv")
data<-data.frame(data)
head(data,5)

```


```{r}
bmi <- data$BMI
bmi.ecdf<-ecdf(bmi)
plot(bmi.ecdf)
```
```{r}
bmi.ecdf(100)-bmi.ecdf(25)
```


##80 percent of the people in this dataset is overweight or obese

```{r}
n<-length(bmi)
B=3000
library(bootstrap)
median.boot<-bootstrap(bmi,B,median)
hist(median.boot$thetastar)
```


```{r}
se_boot <- var(median.boot$thetastar)
theta_hat <- median(bmi)
```
#Confidence Intervals:
1)Normal

```{r}
normal.ci<-c(theta_hat-2*se_boot,theta_hat+2*se_boot)
normal.ci
```
2) Pivotal CI
```{r}
pivotal.ci<-c(2*theta_hat - quantile(median.boot$thetastar,0.975),2*theta_hat - quantile(median.boot$thetastar,0.0275))
pivotal.ci
```
3) Quantile CI
```{r}
quantile.ci<-quantile(median.boot$thetastar,c(0.025,0.975))
quantile.ci
```

Now there are two gender informations here. We want to calculate the mean bmi of each gender and want to know if if differs for male and female. 
#MLE of mu1 minus mu2
```{r}
male_bmi <- data[which(data$Gender=='Male'),"BMI"]
female_bmi <- data[which(data$Gender=='Female'),"BMI"]
```
```{r}
mu1<-mean(male_bmi) #male bmi mean
mu2<-mean(female_bmi) #female bmi mean
mudiff_hat <- mu1-mu2
mudiff_hat
```
#Paramteric bootstrap to calculate CI for mu1-mu2
```{r}
var1<-var(male_bmi)
var2<-var(female_bmi)
sd1<-sqrt(var1)
sd2<-sqrt(var2)
n_male <- length(male_bmi)
n_female <- length(female_bmi)

mu_diff_par<-c()
for (i in 1:1000){
  x <- rnorm(n_male,mu1,sd1)
  y <- rnorm(n_female,mu2,sd2)
  mu_diff_par[i]<-mean(x)-mean(y)
}

mu_diff_par.mean <- mean(mu_diff_par)
mu_diff_par.sd<-sd(mu_diff_par)
CI<-c(mu_diff_par.mean-1.96*mu_diff_par.sd, mu_diff_par.mean+1.96*mu_diff_par.sd)
CI
```
```{r}
hist(mu_diff_par)
```

```{r}
z <- mudiff_hat - 0/(sqrt((var1+var2)/n_male+n_female))
p_value <- 2*(1-pnorm(z))
p_value
```

we cannot reject the null hypothesis which means bmi of the two populations are equal.

Considering flat prior for the mean difference we generate posterior of mu1-mu2
```{r}
mu_diff_var <- var1+var2
posterior_mudiff<-rnorm(n_male+n_female,mudiff_hat,sqrt(mu_diff_var/(n_male+n_female)))
hist(posterior_mudiff)
```

